SMASH companion source code repository

### 2018-12-20 analysis/index.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))
I have an initial setup of the Shiny server document.
wflow_publish("index.Rmd")

3. [Interactive (Shiny) plot for browsing results of Gaussian mean estimation experiments.](gauss_shiny.html)

@@

3. Poisson-distributed data.

@@

See here for the source repository. This is what you will find in the
repository:

*Fill out this section.*

@@

All source code and software in this repository are made available
under the terms of the [MIT license][mit-license]. See the
[LICENSE](LICENSE) file for the full text of the license.

@@

[smash-github]: https://github.com/stephenslab/smash-paper
[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: http://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu

>>>>

3. [Interactive ("Shiny") plot for exploring results of Gaussian mean estimation experiments.](gauss_shiny_setup.html)

@@

5. [Summary of results from Poisson simulations.](poisson.html)

@@

See [here][gtexresults] for the source repository. This is what
you will find in the repository:

```
├── analysis
├── code
├── data
├── docs
├── output
└── workflows
```

+ The **analysis** contains R Markdown source files for the workflowr
  website, including R code used in the final step of the analysis to
  generate figures and tables for the manuscript.

+ The **code** directory contains additional supporting code for the
  analyses.

+ The **data** directory contains original and processed data files
  used in the mash analysis of the GTEx data, example data sets used
  to illustrate the data processing and analysis pipelines, and
  additional data used to generate the tables and figures for the
  manuscript.

+ The **docs** directory contains webpages generated from the R
  Markdown files in the analysis directory.

+ The **output** stores outputs from data processing and analysis
  pipelines ("workflows").

+ The **workflows** directory contains source code ("SoS workflows")
  and Docker configuration files ("Dockerfiles") implementing a data
  processing pipeline for mash and an end-to-end analysis of the GTEx
  data using the multivariate statistical methods ("mash").

@@

Our numerical comparisons make use of some of the functions from
[WaveLab][wavelab], so we have included the WaveLab source code in
this repository. See the `COPYING.m` Wavelab850 subdirectory for more
information about distributing WaveLab.

Our numerical comparisons also use of some functions from
[waveden][waveden], so we have included the GaussianWaveDen source in
this repository. For information about distributing GaussianWaveDen,
see the `copyright.m` in the WavDen subdirectory. Note that we made
one small improvement to the code in `blockJS.m` to prevent an error
that occurs when running the code in newer versions of MATLAB.

All other source code and software in this repository are made
available under the terms of the [MIT license][mit-license]. See the
`LICENSE` file in the git repository for the full text of the license.

@@

[smash-github]: https://github.com/stephenslab/smash-paper
[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: http://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[wavelab]: http://statweb.stanford.edu/~wavelab
[waveden]: http://www-ljk.imag.fr/SMS/software/GaussianWaveDen/down.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu
